### 2018-02-16 doc/manuscript.Rmd
ggplot2 and patchwork to setup chunk

```{r setup, message=FALSE, echo=FALSE}
devtools::load_all('.')
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ds0yr <- project_data %>% 
    filter(VN == 0)
```

>>>>

```{r setup, message=FALSE, echo=FALSE}
devtools::load_all('.')
library(ggplot2)
library(patchwork)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ds0yr <- project_data %>% 
    filter(VN == 0)
```
